---
title: "T2 example RMD"
author: "Christos Oikonomou, Panos Mavrokonstantis, Varun Karamshetty"
date: "01/22/2019"
output:
  html_document: default
  pdf_document: default
---
>This *.rmd file is to help you get started with R Markdown. Notice that there can both text and code in the file.  R Markdown files can be used as a template to generate and update reports with minimal work as new data arrives. 
*In a well written \*.rmd file, just point to the dataset and click "knit" for a fresh report.* 

Let's start writing our report. 

#Data Description

##Structure of the data

In this section we will examine the structure of our data. Below is the structure of our raw data. 

```{r, echo=FALSE}
if("pacman" %in% rownames(installed.packages()) == FALSE) {install.packages("pacman")} # Check if you have universal installer package, install if not

pacman::p_load("caret","ROCR","lift","glmnet","MASS","e1071",'dplyr',
               "partykit","rpart") #Check, and if needed install the necessary packages

STCdata_A<-read.csv("C:\\Users\\MBA\\Dropbox\\Fabio\\MBA\\6 - INSEAD\\11 - Courses\\P3\\DSB - Data Science for Business\\!Tutorials\\#2/0506 STC(A) data_numerical dates.csv") 


str(STCdata_A) # See if some data types were misclassified when importing data from CSV
```

##Data Preprocessing
We need to fix the type of the data

```{r, echo=TRUE}
STCdata_A$From.Grade <- as.factor(STCdata_A$From.Grade)
STCdata_A$To.Grade <- as.factor(STCdata_A$To.Grade)
STCdata_A$Is.Non.Annual. <- as.factor(STCdata_A$Is.Non.Annual.)
STCdata_A$Days <- as.factor(STCdata_A$Days)
STCdata_A$CRM.Segment <- as.factor(STCdata_A$CRM.Segment)
STCdata_A$Parent.Meeting.Flag <- as.factor(STCdata_A$Parent.Meeting.Flag)
STCdata_A$MDR.High.Grade <- as.factor(STCdata_A$MDR.High.Grade)
STCdata_A$School.Sponsor <- as.factor(STCdata_A$School.Sponsor)
STCdata_A$NumberOfMeetingswithParents <- as.factor(STCdata_A$NumberOfMeetingswithParents)
STCdata_A$SingleGradeTripFlag <- as.factor(STCdata_A$SingleGradeTripFlag)
STCdata_A$Retained.in.2012. <- as.factor(STCdata_A$Retained.in.2012.)
```

Create a custom function to fix missing values ("NAs") and preserve the NA info as surrogate variables

```{r, echo=TRUE}
fixNAs<-function(data_frame){
  # Define reactions to NAs
  integer_reac<-0
  factor_reac<-"FIXED_NA"
  character_reac<-"FIXED_NA"
  date_reac<-as.Date("1900-01-01")
  # Loop through columns in the data frame and depending on which class the variable is, apply the defined reaction and create a surrogate
  
  for (i in 1 : ncol(data_frame)){
    if (class(data_frame[,i]) %in% c("numeric","integer")) {
      if (any(is.na(data_frame[,i]))){
        data_frame[,paste0(colnames(data_frame)[i],"_surrogate")]<-
          as.factor(ifelse(is.na(data_frame[,i]),"1","0"))
        data_frame[is.na(data_frame[,i]),i]<-integer_reac
      }
    } else
      if (class(data_frame[,i]) %in% c("factor")) {
        if (any(is.na(data_frame[,i]))){
          data_frame[,i]<-as.character(data_frame[,i])
          data_frame[,paste0(colnames(data_frame)[i],"_surrogate")]<-
            as.factor(ifelse(is.na(data_frame[,i]),"1","0"))
          data_frame[is.na(data_frame[,i]),i]<-factor_reac
          data_frame[,i]<-as.factor(data_frame[,i])
          
        } 
      } else {
        if (class(data_frame[,i]) %in% c("character")) {
          if (any(is.na(data_frame[,i]))){
            data_frame[,paste0(colnames(data_frame)[i],"_surrogate")]<-
              as.factor(ifelse(is.na(data_frame[,i]),"1","0"))
            data_frame[is.na(data_frame[,i]),i]<-character_reac
          }  
        } else {
          if (class(data_frame[,i]) %in% c("Date")) {
            if (any(is.na(data_frame[,i]))){
              data_frame[,paste0(colnames(data_frame)[i],"_surrogate")]<-
                as.factor(ifelse(is.na(data_frame[,i]),"1","0"))
              data_frame[is.na(data_frame[,i]),i]<-date_reac
            }
          }  
        }       
      }
  } 
  return(data_frame) 
}
```

Create another a custom function to combine rare categories into "Other."+the name of the original variable (e.g., Other.State)

```{r, echo=TRUE}
# This function has two arguments: the name of the dataframe and the count of observation in a category to define "rare"
combinerarecategories<-function(data_frame,mincount){ 
  for (i in 1 : ncol(data_frame)){
    a<-data_frame[,i]
    replace <- names(which(table(a) < mincount))
    levels(a)[levels(a) %in% replace] <-paste("Other",colnames(data_frame)[i],sep=".")
    data_frame[,i]<-a }
  return(data_frame) }

```

Apply the fixNAs and combinerarecategories functions to the data and then split it into testing and training data.

```{r, echo=TRUE}
STCdata_A<-fixNAs(STCdata_A)
STCdata_A<-combinerarecategories(STCdata_A,10) #combine categories with <10 values in STCdata into "Other"

set.seed(77850) #set a random number generation seed to ensure that the split is the same everytime
inTrain <- createDataPartition(y = STCdata_A$Retained.in.2012.,
                               p = 1888/2389, list = FALSE)
training <- STCdata_A[ inTrain,]
testing <- STCdata_A[ -inTrain,]
```

# CTREE

## Train model

```{r, echo=TRUE, fig.width = 14}
ctree_tree<-ctree(Retained.in.2012.~.,data=training) #Run ctree on training data
plot(ctree_tree, gp = gpar(fontsize = 8)) #Plotting the tree (adjust fontsize if needed)
```

## Estimating confusion matrix

```{r, echo=TRUE}
ctree_prediction<-predict(ctree_tree,newdata=testing, type="response") 
confusionMatrix <- confusionMatrix(ctree_prediction,testing$Retained.in.2012., positive = "1") #Display confusion matrix
accuracy <- confusionMatrix$overall["Accuracy"]
confusionMatrix
```

## ROC Curve
```{r, echo=TRUE, fig.width = 14}
ctree_probabilities_testing <-predict(ctree_tree,newdata=testing,type = "prob") #Predict probabilities
ctree_pred_testing <- prediction(ctree_probabilities_testing[,2], testing$Retained.in.2012.) #Calculate errors
ctree_ROC_testing <- performance(ctree_pred_testing,"tpr","fpr") #Create ROC curve data
plot(ctree_ROC_testing) #Plot ROC curve
```

## AUC (area under curve)
```{r, echo=TRUE, fig.width = 14}
auc.tmp <- performance(ctree_pred_testing,"auc") #Create AUC data
ctree_auc_testing <- as.numeric(auc.tmp@y.values) #Calculate AUC
ctree_auc_testing #Display AUC value: 90+% - excellent, 80-90% - very good, 70-80% - good, 60-70% - so so, below 60% - not much value
```

## Lift chart
```{r, echo=TRUE, fig.width = 14}
plotLift(ctree_prediction,  testing$Retained.in.2012., cumulative = TRUE, n.buckets = 10) # Plot Lift chart
```
